Regular singular Volterra equations on complex domains

### 2023-08-15 reg-sing-volterra.tex
Rewrite main results overview from fixed-point perspective
Also, keep working on the argument that the prototype solution is equivalent to
zeta^(tau - 1) modulo less singular stuff.

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
In this section, we'll prove the results stated in Section~\ref{sec:results}. Our arguments will follow the process of solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by Picard iteration.

@@

To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$. In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\Omega)$. The perturbed operator $\volterra$ therefore sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$.

@@

We can now see that at each stage of the Picard iteration process, we start with an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives 
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$, and $\softpart f_0$ has been smoothed and it lies in the same function space as $\solptb$. The contraction mapping theorem guarantees the existence and uniqueness of the fixed point 
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.

\color{RoyalBlue}
We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives us the new approximate solution
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$ but also augmented with another $\softpart \solproto$. The contraction mapping theorem guarantees that these opposing processes will eventually balance out, bringing us to a unique fixed point where
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.
\color{black}
%%To prove that the Picard iteration process converges, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ shrinks perturbations

@@

\subsection{How $\softpart$ perturbs the prototype solution \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}

@@

\subsection{Showing that $\volterra$ shrinks perturbations \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
\subsubsection{Overview}
In this section, we'll prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.

@@

We now know that by setting $\Lambda > \lambda + \textcolor{orange}{\delta}^{-1} \max\{1, (1/5)^{\rho-1}\}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. \textcolor{orange}{[I think this explicit bound only accounts for the integral over the end of the path, $t \in [1/5, 1)$. To ensure that the whole integral is less than $1$, we also need to look at the integral over the beginning of the path, $t \in (0, 1/5]$, which is calculated above. To me, that seems to make the bound too complicated to be worth stating---but maybe you can find a simplification.]} This completes our proof of Proposition~\ref{prop:get-contraction}.
\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
\begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$. Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter. Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.

@@

    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ \textcolor{magenta}{[to get this from our uniqueness result, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]} and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$. The result holds for every critical point of $P$. 
\end{thm}

@@

\begin{align*}
  f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
  &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)
  %  &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
\end{align*}
Expanding $p(a)$ near $\zeta=\alpha$,

\begin{align*}
     \frac{(\zeta(a)-\alpha)^{\tau_\alpha-1}}{p'(a)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right) 
\end{align*}

>>>>

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$. We'll now show that the method works by proving those results.

We start by constructing the prototype solution $\solproto$ from the kernel of $\hardpart$, which is the separable operator that gives $\volterra = \hardpart + \softpart$ its regular singularity. We'll show in Section~\ref{sec:proto-construction-regularity} that $\solproto$ satisfies the equation $\solproto = \hardpart \solproto$ and belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.

To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$. In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\domain)$.

Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there. To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\epsilon}{\Lambda}(\domain)$ when $\Lambda$ is large enough. This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.

%%In Section~\ref{setting}, we built $\volterra$ by taking a separable operator $\hardpart$ with a regular singularity at $\zeta = 0$ and adding a perturbation $\softpart$. Correspondingly, our solution method starts with the prototype solution $\solproto$,

%%In this section, we'll prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the Volterra equation $\solwhole = \volterra \solwhole$ from Section~\ref{setting}. Recall that $\volterra$ is the sum of a separable operator $\hardpart$, which has a regular singularity at $\zeta = 0$, and a perturbation $\softpart$.

\color{SeaGreen}
In this section, we'll prove the results stated in Section~\ref{sec:results}. Our arguments will follow the process of solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by Picard iteration.

@@

To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$. In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\domain)$. The perturbed operator $\volterra$ therefore sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$.

@@

\color{RoyalBlue}
We can now see that at each stage of the Picard iteration process, we start with an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives 
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$, and $\softpart f_0$ has been smoothed and it lies in the same function space as $\solptb$. The contraction mapping theorem guarantees the existence and uniqueness of the fixed point 
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.

\color{MediumBlue}
We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
\[ \solproto + \solptb, \]
with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives us the new approximate solution
\[ \solproto + \softpart \solproto + \volterra \solptb, \]
where the perturbation $\solptb$ has been contracted by $\volterra$ but also augmented with another $\softpart \solproto$. The contraction mapping theorem guarantees that these opposing processes will eventually balance out, bringing us to a unique fixed point where
\[ \solptb = \softpart \solproto + \volterra \solptb. \]
We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.
\color{black}
%%To prove that the Picard iteration process converges, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ shrinks perturbations

@@

\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}

@@

\subsection{Showing that $\volterra$ shrinks less singular functions \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
\subsubsection{Overview}
In this section, we'll prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.

@@

We now know that by setting $\Lambda > \lambda + \textcolor{orange}{\delta}^{-1} \max\{1, (1/5)^{\rho-1}\}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$. \textcolor{orange}{[I think this explicit bound only accounts for the integral over the end of the path, $t \in [1/5, 1)$. To ensure that the whole integral is less than $1$, we also need to look at the integral over the beginning of the path, $t \in (0, 1/5]$, which is calculated above. To me, that seems to make the bound too complicated to be worth stating---but maybe you can find a simplification.]} This completes our proof of Proposition~\ref{prop:get-contraction}.
\subsection{Existence and uniqueness of a fixed point \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
\begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$. Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter. Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.

@@

    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$. The result holds for every critical point of $P$. 
\end{thm}

 \textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}

@@

\begin{align*}
  f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
  &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)
  %  &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
\end{align*}
Expanding $p(a)$ near $\zeta=\alpha$, we find that $f_{0,\alpha}$ is proportional to

\begin{align*}
\frac{(\zeta(a)-\alpha)^{\tau_\alpha-1}}{p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...} \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right)
\end{align*}
where both the exponential and the denominator are bounded as $\zeta(a)$ approaches $\alpha$.

\color{DarkTurquoise}
From Condition~\eqref{cond:sing}, we have
\[ \left| \frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} \right| < \varepsilon \]
in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that
\[ S(a) = \int_{\zeta = \alpha}^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta \]
converges for $a \in \domain_\text{near}$, so we have
\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
for $a \in \domain_\text{near}$. Observe that $|S| \le \varepsilon |\zeta - \alpha|$ in $\domain_\text{near}$.

The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$ and

\[
\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq 
\]

We should be able to deduce from this that
\begin{align*}
f_{0,\alpha} & \in \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} O(|\zeta - \alpha|) \\
& \subset \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,O\big(|\zeta-\alpha|^{\tau_\alpha}\big) \\
\end{align*}
when we restrict to $\domain_\text{near}$.
\color{black}
\end{proof}
